Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-03 ms/manuscript.Rmd
Add check on statement about conditional AIC

>>>>

```{r discus-model-stats}
# Check that conditional AIC was lower in the reproductive model compared to the environmental model for SES of RPD and SES of PD
# Split aic_env_repro dataframe into nested list for easier indexing
c_aic <- aic_env_repro %>% split(.$resp_var) %>% map(~split(., .$model_type))
assert_that(c_aic$pd_obs_z$percent_apo$conditional_aic < c_aic$pd_obs_z$temp$conditional_aic)
assert_that(c_aic$rpd_obs_z$percent_apo$conditional_aic < c_aic$rpd_obs_z$temp$conditional_aic)
```
